Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-03-29 src-latex/parts/20-related-work.tex
Update missing comments

The directory processing pipeline presented in \cite{bell2020automated} includes an OCR step, done with Tesseract, and a NER step to identify company names and addresses, performed using regular expressions.
This section reviews existing OCR and NER approaches on historical texts and presents some works assessing the effects of OCR quality on the NER performance and the proposed solutions.

>>>>

The directory processing pipeline presented in \cite{bell2020automated} and illustrated in \cref{fig.pipeline-overview}, includes an OCR step done with Tesseract, and a NER step to identify company names and addresses, performed using regular expressions.
This section reviews existing OCR and NER approaches on historical texts and presents some works assessing the effects of OCR quality on the NER performance and the proposed solutions.

### 2022-03-29 src-latex/parts/30-dataset.tex
Add links and refs to dataset
Update missing comments

This section presents the historical sources that we selected and their contents. It also details the construction of the groundtruth dataset leveraged in our experiments and the metrics used to evaluate OCR and NER results.

@@

The directories are available from different libraries in Paris and have been digitised independently in various levels of quality. 
They cover a large period of time and originate from several publishers.
Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see fig. \ref{fig:directories}).
We want our groundtruth dataset to be representative of the diversity of directories available in the period.

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/eval-ocr-ner.pdf}
    \caption{OCR and NER evaluation protocol example.}
    \label{fig.eval-ocr-ner}
\end{figure}

>>>>

This section presents the historical sources that we selected and their contents.
It also details the construction of the groundtruth dataset leveraged in our experiments and the metrics used to evaluate OCR and NER results.
The resulting dataset is publicly available~\cite{abadie_dataset_22} under the permissive \emph{Creative Commons Attribution 4.0 International} licence.

@@

The directories are available from different libraries in Paris and have been digitised independently in various levels of quality. 
They cover a large period of time and originate from several publishers.
Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see \cref{fig:directories}).
We want our groundtruth dataset to be representative of the diversity of directories available in the period.

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/eval-ocr-ner.pdf}
    \caption{OCR and NER evaluation protocol example. The OCR prediction is first aligned on the GOLD text to get the
    OCR quality. The same alignment is used to project the GOLD tags on the OCR prediction. Projected tags enable
    the NER system run on the OCR predicted text to be assessed.}
    \label{fig.eval-ocr-ner}
\end{figure}

### 2022-03-29 src-latex/parts/50-xp-setup-BACKUP.tex
Update missing comments

\subsection{Experiment 2: Impact of OCR nosie on named entity recognition}
\label{subsection:experiment-2-setup}
Noise introduced by OCR is known to impede the named entity recognition process (see section~\ref{subsection:stoa-ner-on-historical-texts}).
%The second experiment assesses the impact of the OCR on the quality of the NER results.
The second experiment addresses two questions (1) which model is the most robust to OCR noise and (2) what is the most appropriate strategy to fine-tune the NER layer if the input texts to label are noisy ?
To this end, we leverage the labeled OCR datasets produced following to the method explained in Section 5, in addition to the gold reference.

>>>>

\subsection{Experiment 2: Impact of OCR nosie on named entity recognition}
\label{subsection:experiment-2-setup}
Noise introduced by OCR is known to impede the named entity recognition process (see \cref{subsection:stoa-ner-on-historical-texts}).
%The second experiment assesses the impact of the OCR on the quality of the NER results.
The second experiment addresses two questions (1) which model is the most robust to OCR noise and (2) what is the most appropriate strategy to fine-tune the NER layer if the input texts to label are noisy ?
To this end, we leverage the labeled OCR datasets produced following to the method explained in Section 5, in addition to the gold reference.

### 2022-03-29 src-latex/parts/60-results-BACKUP.tex
Update missing comments

\subsection{Experiment 1: NER sensibility to the number of training examples}
Table \ref{tab:experiment-1-models-performances} and Figure \ref{fig:f1-vs-trainsize} show the mean F1 score, precision, and recall computed on the test dataset, for 5 fine tunings of each model and for each of the 8 training subsets.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the Spacy model.

@@

\begin{figure}[h!]
	   \center{\includegraphics[width=\textwidth]
	       {images/experiment-1-models-performances.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Precision, recall and f1 score from table~\ref{tab:experiment-1-models-performances}}.
\end{figure}

>>>>

\subsection{Experiment 1: NER sensibility to the number of training examples}
\Cref{tab:experiment-1-models-performances} and \cref{fig:f1-vs-trainsize} show the mean F1 score, precision, and recall computed on the test dataset, for 5 fine tunings of each model and for each of the 8 training subsets.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the Spacy model.

@@

\begin{figure}[h!]
	   \center{\includegraphics[width=\textwidth]
	       {images/experiment-1-models-performances.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Precision, recall and f1 score from \cref{tab:experiment-1-models-performances}}.
\end{figure}
